Assessment of forestry road network projection methods using the “roads” package in R

### 2022-10-14 analysis/paper/paper.Rmd
remove part about rivers since I don't think there cost was actually included.
Use cost with existing roads burned in for fig 1

```{r fig1, fig.cap="Revelstoke timber supply area in British Colombia, Canada. The colour shows the cost of building roads across each pixel.", cache=TRUE}
tsaBoundary <- read_sf(here(data_path_raw, "tsa27_boundaries.gpkg"))
#cost surface raster layer
bc_cost_surface <- terra::rast(here(data_path_raw, "cost_surface_bc_ha.tif"))
lakeValue <- 65000

tsaCost <- terra::crop(bc_cost_surface, tsaBoundary)
tsaCost <- terra::subst(tsaCost, from = NA, to = lakeValue)
tsaCost <- terra::mask(tsaCost, terra::vect(tsaBoundary))

@@

To spatially define the cost of constructing and traveling on a forestry road we developed a cost raster. We used several spatial raster layers to construct our cost surface. Following the Interior Appraisal Manual of BC, the base cost per kilometer of road was a linear function of slope [@governmentofbritishcolumbia2021a]. Separate costs for river and pipeline crossings were then added and major water bodies were considered barriers and assigned a very high cost. Lastly, existing roads were assigned a cost of 0 (Table 1). The cost raster produced consists of 1703936 pixels with a resolution of 100 meters by 100 meters.

@@

```{r}
tbl <- "Cost Type|Road Attribute|Value ($ per km)|Source
Barriers of road development|Major lakes|65000|Major water bodies of BC
Impedance|Existing roads|0|Assumed
Road Construction Cost Structure|Pipe crossing|1911|Interior Appraisal Manual
|River crossing|2130|Interior Appraisal Manual
|Base cost|16178 + 504*slope|Interior Appraisal Manual
"
df <- read.delim(textConnection(tbl),header=FALSE,sep="|",strip.white=TRUE,stringsAsFactors=FALSE)
names(df) <- unname(as.list(df[1,]))
df <- df[-1,] # remove first row
row.names(df)<-NULL
knitr::kable(df)
```

>>>>

```{r fig1, fig.cap="Revelstoke timber supply area in British Colombia, Canada. The colour shows the cost of building roads across each pixel.", cache=TRUE}
tsaBoundary <- read_sf(here(data_path_raw, "tsa27_boundaries.gpkg"))
#cost surface raster layer
tsaCost <- terra::rast(here(data_path_drvd, "input_cost.tif"))

tsaCost <- terra::mask(tsaCost, terra::vect(tsaBoundary))

@@

To spatially define the cost of building and traveling on a forestry road we developed a simple cost raster based on the slope and major barriers. Following the Interior Appraisal Manual of BC, the base cost per kilometer of road was a linear function of slope [@governmentofbritishcolumbia2021a]. Major water bodies were considered barriers and assigned a very high cost. Lastly, existing roads were assigned a cost of 0 (Table 1). The cost raster produced consists of 1703936 pixels with a resolution of 100 meters by 100 meters.

@@

```{r}
tbl <- "Cost Type|Value ($ per km)|Source
Slope|16178 + 504*slope|Interior appraisal manual
Major lakes|65000|Major water bodies of BC
Existing roads|0|Digital road atlas and forest tenure roads for BC
"
df <- read.delim(textConnection(tbl),header=FALSE,sep="|",strip.white=TRUE,stringsAsFactors=FALSE)
names(df) <- unname(as.list(df[1,]))
df <- df[-1,] # remove first row
row.names(df)<-NULL
knitr::kable(df)
```
